---
title: "trophic.sdm.data: preparing data for European Vertebrates trophic SDM"
output: github_document
---


```{r echo=FALSE, message=FALSE, results="hide"}
options(Encoding="UTF-8")
library(badger)
```


<!-- `r badger::badge_cran_release("segclust2d", "orange")` -->
<!-- `r badger::badge_cran_download("segclust2d", "grand-total", "yellow")` -->
`r badger::badge_github_version("rpatin/trophic.sdm.data", "blue")`
`r badger::badge_last_commit("rpatin/trophic.sdm.data")`

# Introduction


# News 
## v0.1.0 First Release (29/08/2023)
- Fixed and completed documentation
- Bugfix to summary function

## v0.0.5 (pre-release)
### Features
- calculation of aggregated prey metrics
- mixed workflow (backup IUCN) is possible to parameterize:
  - when not enough occurrences are present in gbif
  - when gbif extraction failed
  - when certainty threshold are too low
  - when there are too high proportion of uncertain cell within IUCN range
- improved and speed up workflow using raster to calculate aggregated prey metrics
- improved show method for trophic_dataset
- added overwrite options

## v0.0.4 (12/06/2023)
- support for multiple resolutions
- workflow for IUCN
- improved subsampling
- improved workflow 

## v0.0.3
- subsampling of absences outside IUCN distribution
- support for filtering atlas data 

## v0.0.2 - Bugfix Release (22/02/2023)

### bugfix
- threshold are now always discrete values
- buffer_iucn only create non-existing files

## v0.0.1 - First Release (21/02/2023)

### Release feature
- workflow for trophic dataset based on gbif data
- detection of taxonomic conflicts within trophic groups with `detect_taxonomic_conflict()`. i.e. predator with some prey within the same 
trophic groups but with very different taxonomy (that would be problematic to mix 
in a trophic sdm)
- detection of gbif observation outside of IUCN ranges and diagnostic of the distance 
to IUCN distribution.
- calculation of gbif sampling effort
- buffer calculation for IUCN polygon ranges

### Missing features
- no support for filtering atlas data & multiple resolutions
- no workflow for IUCN
- no evaluations
- no subsampling
- no calculation of aggregated prey metrics
- no splitting of trophic group in metaweb


# Installation

If you want the newest `r badger::badge_devel("rpatin/trophic.sdm.data", "blue")`, you
can install `trophic.sdm.data` from github  with:

```{r, eval=FALSE}
devtools::install_github("rpatin/trophic.sdm.data")
```

