---
title: "trophic_sdm_data: preparing data for European Vertebrates trophic SDM"
output: github_document
---


```{r echo=FALSE, message=FALSE, results="hide"}
options(Encoding="UTF-8")
library(badger)
```


<!-- `r badger::badge_cran_release("segclust2d", "orange")` -->
<!-- `r badger::badge_cran_download("segclust2d", "grand-total", "yellow")` -->
`r badger::badge_github_version("rpatin/trophic_sdm_data", "blue")`
`r badger::badge_last_commit("rpatin/trophic_sdm_data")`

# Introduction


# News 

Pre-Release Features (v. 0.0.1)
- workflow for trophic dataset based on gbif data
- detection of taxonomic conflicts within trophic groups with `detect_taxonomic_conflict()`. i.e. predator with some prey within the same 
trophic groups but with very different taxonomy (that would be problematic to mix 
in a trophic sdm)
- detection of gbif observation outside of IUCN ranges and diagnostic of the distance 
to IUCN distribution.
- calculation of gbif sampling effort
- buffer calculation for IUCN polygon ranges

# Installation

If you want the newest `r badger::badge_devel("rpatin/trophic_sdm_data", "blue")`, you
can install `trophic_sdm_data` from github  with:

```{r, eval=FALSE}
devtools::install_github("rpatin/trophic_sdm_data")
```

